---
title: "General Prediction of the 2019 Canadian Federal Election if ‘everyone’ had voted"
author: "Xinyun Zhang, ID1004712563"
date: "08/12/2020"
output: pdf_document
---

# Abstract
Voting and elections are crucial to one nation's democracy. Therefore, a study on 2019 Canadian Federal Election has been made in the sections below. By building multi-level regression with post-stratification on 2019 CES and 2017 GSS data, the predicted outcome of the 2019 Canadian Federal Election under the assumption that everyone over 18 has voted would be made. From the models and results of BIC, the importance of factors that might impact the preference of voter will be analyzed as well. Generally, this analysis demonstrates the relationship between voters' characterization and the outcome of the election. 

# Keywords
2019 Canadian Federal Election, turnout, multi-level regression, post-stratification, linear regression, logstic regression, BIC.

# 1. Introduction
As the most essential elements of democracy are voting and elections, the Canadian Election Study that contains a large-scale survey of citizens is useful for analyzing the electoral democracy in Canada(Welcome to the 2019 Canadian Election Study, 2019). The citizens’ preferences towards main political issues could infer the political behaviors and attitudes of Canadians. Since factors like age, education and gender are all associated with voting(Factors associated with voting, 2015). As the Liberal Party and the Conservative Party always have been the main opposition rivals to each other during the election. Some people may wonder that how the outcome would have been different if everyone beyond 18 who leaves valid answers(no NA) to the 2019 CES had voted. The importance of turnout will be predicted based on this assumption in further analysis.

As the survey data was collected by non-probability sampling, the multi-level regression with post-stratification(MRP) could be a good way to predict election results among different factors. MRP is a statistical technique that builds models to estimate public opinions for defined geographic areas from the survey results(Masters, 2019). In this report, MRP will be used under the assumption that people with similar features share similar constituency opinion toward the election. A model with several variables from survey data will be built to check the effect of the variables on the probability of voting for Justin Trudeau’s Liberals. Then, making the post-stratification analysis based on census data. By performing the proportion of each characteristic and calculating the predicted probability of voting for the Liberal Party within each cell, an estimation of voting intention for certain constituency could be given.

Based on the Global News polling conducted by Ipsos, the voting intentions of men and women in distinct segmenting generations were quite different(Ipsos, 2019). For the winner Liberal Party, support seems no differences regardless of age or gender. However, young women prefer to vote for Jagmeet Singh’S NDP, while young men were much more likely to vote for Andrew Scheer’s Conservatives. What’s more, men in younger years appear less propensity to vote than women, but in their older years, men have a stronger tendency to vote on election day.

In the sub-sections below, two data sets including 2019 Canadian Election Online Survey (CES) and 2017 Canadian General Social Survey(GSS) will be utilized to investigate how the outcome would have been different if everyone over 18 who leaves valid answers(no NA) to the 2019 CES had voted. In the Methodology section, a table with key components of the data and model for the election analysis will be described. Results under the assumptions are provided in the Results section. The overall discussion including a summary, a conclusion, weaknesses and future steps of the study are present at the end.

# 2. Methodology
This report is interested in predicting the voting outcome of 2019 Canadian Election by online survey data from 2019 CES. As Justin Trudeau from Liberal Party and Andrew Scheer the Conservative Party are two candidates who gained the most support during the 2019 Canadian Federal Election. For the sub-sections below, two logistic models for these two parties will be built with four variables from the survey data, including gender, province, whether born in Canada and age group. The effect of each variable on the probability of voting for these two parties will be analyzed as well.

What's more, the post-stratification analysis will be made based on the census data from the 2017 Canadian General Social Survey. The data will first be separated into four cells based on the four chosen variables. The proportions of voting Liberals and Conservatives within each cell will be performed correspondingly. Then, calculations of the total prediction probability for these two parties will be made. By comparing the result, the new result under the assumptions could be concluded.

Additionally, two fitted linear models could be built by using backward elimination with BIC. Since BIC penalizes model complexity, it is a helpful tool to sift out significant variables to the model. Important factors that may influence the outcome of the election could be estimated from linear models. 

## 2.1 Data
A data wrangling process is made in this section. The author makes specific selections of the following four types of independent variables for further analysis:
1. gender: the gender of the voter
2. province: constituency
3. age_group: age between 18 to 34 is youth group, while elderly group include those 35 and above
4. born_in_canada: whether born in Canada 

In order to distinguish the specific voting trend of youth and elderly groups, the variable 'age_group' was used rather than the variable 'age'. As one person during different phases of life could have opposite views toward the same thing, opinions from distinct age groups seem more essential to display the general perspective toward the candidates. Additionally, the ages recorded in 2017 GSS were all added by two to form a new column of 'age2019'. New column of data will be used for further analysis which makes assumptions of two data sets to be similar. 

These variables are chosen based on the background information of the election that was introduced previously in Section One. As males and females within different age groups may have distinct opinions of voting (Ipsos, 2019),  and constituency opinions of people from different provinces are distinct. Therefore, the resulting data sets with the key components are shown below.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# devtools::install_github("hodgettsp/cesR", force=TRUE)
# load cesR package and labelled package
library(cesR)
library(labelled)
library(tidyr)
library(tidyverse)
library(knitr)
library(janitor)
library(table1)
```

```{r, include=FALSE}
# call 2019 CES online survey
cesR::get_ces("ces2019_web")

# convert values to factor type
ces2019_web <- to_factor(ces2019_web)
head(ces2019_web)

# rename
reduced_data <- 
  ces2019_web %>% 
  select(cps19_yob,
         cps19_gender,
         cps19_province,
         cps19_votechoice,
         cps19_bornin_canada)
reduced_data <- 
  reduced_data %>% 
  clean_names() %>% 
  rename(birthyear=cps19_yob,
         gender0=cps19_gender,
         province=cps19_province,
         votechoice=cps19_votechoice,
         bornin_canada=cps19_bornin_canada)
# survey data cleaning
reduced_data <- 
  reduced_data %>%
  mutate(vote_liberal = 
           ifelse(votechoice=="Liberal Party", 1, 0))  %>%
  mutate(vote_conservative = 
           ifelse(votechoice=="Conservative Party", 1, 0)) %>%
  mutate(age = as.numeric(birthyear),
         age_group= cut(age, 
                          breaks=c(18,34, Inf),
                          labels=c('18-34 youth', '35+ elder'))) %>% 
        
  mutate(gender = if_else(gender0=="A woman","Female",
                          if_else(gender0=="A man","Male","Other")))

reduced_data <- na.omit(reduced_data)

write_csv(reduced_data, "survey_data.csv")
```

```{r,include=FALSE}
# get gss Data
raw_data <- read_csv("AAqOnyiY.csv")
dict <- read_lines("gss_dict.txt", skip = 18)
labels_raw <- read_file("gss_labels.txt")
# Set-up the dictionary
variable_descriptions <- as_tibble(dict) %>% 
  filter(value!="}") %>% 
  mutate(value = str_replace(value, ".+%[0-9].*f[ ]{2,}", "")) %>% 
  mutate(value = str_remove_all(value, "\"")) %>% 
  rename(variable_description = value) %>% 
  bind_cols(tibble(variable_name = colnames(raw_data)[-1]))
# set variable name and the possible values
labels_raw_tibble <- as_tibble(str_split(labels_raw, ";")[[1]]) %>% 
  filter(row_number()!=1) %>% 
  mutate(value = str_remove(value, "\nlabel define ")) %>% 
  mutate(value = str_replace(value, "[ ]{2,}", "XXX")) %>% 
  mutate(splits = str_split(value, "XXX")) %>% 
  rowwise() %>% 
  mutate(variable_name = splits[1], cases = splits[2]) %>% 
  mutate(cases = str_replace_all(cases, "\n [ ]{2,}", "")) %>%
  select(variable_name, cases) %>% 
  drop_na()

labels_raw_tibble <- labels_raw_tibble %>% 
  mutate(splits = str_split(cases, "[ ]{0,}\"[ ]{0,}"))
# set-up the regex
add_cw_text <- function(x, y){
  if(!is.na(as.numeric(x))){
    x_new <- paste0(y, "==", x,"~")
  }
  else{
    x_new <- paste0("\"",x,"\",")
  }
  return(x_new)}

cw_statements <- labels_raw_tibble %>% 
  rowwise() %>% 
  mutate(splits_with_cw_text = list(modify(splits, add_cw_text, y = variable_name))) %>% 
  mutate(cw_statement = paste(splits_with_cw_text, collapse = "")) %>% 
  mutate(cw_statement = paste0("case_when(", cw_statement,"TRUE~\"NA\")")) %>% 
  mutate(cw_statement = str_replace(cw_statement, ",\"\",",",")) %>% 
  select(variable_name, cw_statement)
# Clean up the regex
cw_statements <- 
  cw_statements %>% 
  mutate(variable_name = str_remove_all(variable_name, "\\r")) %>% 
  mutate(cw_statement = str_remove_all(cw_statement, "\\r"))
# Apply dictionary to the raw data
gss <- raw_data %>% 
  select(CASEID, 
         agedc, 
         achd_1c, 
         achdmpl, 
         totchdc, 
         acu0c,
         agema1c,
         achb1c,
         rsh_131a,
         arretwk,
         slm_01, 
         sex, 
         brthcan, 
         brthfcan,
         brthmcan,
         brthmacr,
         brthprvc,
         yrarri,
         prv, 
         region, 
         luc_rst, 
         marstat, 
         amb_01, 
         vismin, 
         alndimmg,
         bpr_16, 
         bpr_19,
         ehg3_01b, 
         odr_10, 
         livarr12, 
         dwelc, 
         hsdsizec,
         brthpcan,
         brtpprvc, 
         visminpr,
         rsh_125a, 
         eop_200,
         uhw_16gr,
         lmam_01, 
         acmpryr,
         srh_110,
         srh_115,
         religflg, 
         rlr_110,
         lanhome, 
         lan_01,
         famincg2, 
         ttlincg2, 
         noc1610, 
         cc_20_1,
         cc_30_1,
         ccmoc1c,
         cor_031,
         cor_041,
         cu0rnkc,
         pr_cl,
         chh0014c,
         nochricc,
         grndpa,
         gparliv,
         evermar,
         ma0_220,
         nmarevrc,
         ree_02,
         rsh_131b,
         rto_101,
         rto_110,
         rto_120,
         rtw_300,
         sts_410,
         csp_105,
         csp_110a,
         csp_110b,
         csp_110c,
         csp_110d,
         csp_160,
         fi_110) %>% 
  mutate_at(vars(agedc:fi_110), .funs = funs(ifelse(.>=96, NA, .))) %>% 
  mutate_at(.vars = vars(sex:fi_110),
            .funs = funs(eval(parse(text = cw_statements %>%
                                      filter(variable_name==deparse(substitute(.))) %>%
                                      select(cw_statement) %>%
                                      pull()))))

# Fix the names
gss <- gss %>% 
  clean_names() %>% 
  rename(age = agedc,
         age_first_child = achd_1c,
         age_youngest_child_under_6 = achdmpl,
         total_children = totchdc,
         age_start_relationship = acu0c,
         age_at_first_marriage = agema1c,
         age_at_first_birth = achb1c,
         distance_between_houses = rsh_131a,
         age_youngest_child_returned_work = arretwk,
         feelings_life = slm_01,
         sex = sex,
         place_birth_canada = brthcan,
         place_birth_father = brthfcan,
         place_birth_mother = brthmcan,
         place_birth_macro_region = brthmacr,
         place_birth_province = brthprvc,
         year_arrived_canada = yrarri,
         province = prv,
         region = region,
         pop_center = luc_rst,
         marital_status = marstat,
         aboriginal = amb_01,
         vis_minority = vismin,
         age_immigration = alndimmg,
         landed_immigrant = bpr_16,
         citizenship_status = bpr_19,
         education = ehg3_01b,
         own_rent = odr_10,
         living_arrangement = livarr12,
         hh_type = dwelc,
         hh_size = hsdsizec,
         partner_birth_country = brthpcan,
         partner_birth_province = brtpprvc,
         partner_vis_minority = visminpr,
         partner_sex = rsh_125a,
         partner_education = eop_200,
         average_hours_worked = uhw_16gr,
         worked_last_week = lmam_01,
         partner_main_activity = acmpryr,
         self_rated_health = srh_110,
         self_rated_mental_health = srh_115,
         religion_has_affiliation = religflg,
         regilion_importance = rlr_110,
         language_home = lanhome,
         language_knowledge = lan_01,
         income_family = famincg2,
         income_respondent = ttlincg2,
         occupation = noc1610,
         childcare_regular = cc_20_1,
         childcare_type = cc_30_1,
         childcare_monthly_cost = ccmoc1c,
         ever_fathered_child = cor_031,
         ever_given_birth = cor_041,
         number_of_current_union = cu0rnkc,
         lives_with_partner = pr_cl,
         children_in_household = chh0014c,
         number_total_children_intention = nochricc,
         has_grandchildren = grndpa,
         grandparents_still_living = gparliv,
         ever_married = evermar,
         current_marriage_is_first = ma0_220,
         number_marriages = nmarevrc,
         religion_participation = ree_02,
         partner_location_residence = rsh_131b,
         full_part_time_work = rto_101,
         time_off_work_birth = rto_110,
         reason_no_time_off_birth = rto_120,
         returned_same_job = rtw_300,
         satisfied_time_children = sts_410,
         provide_or_receive_fin_supp = csp_105,
         fin_supp_child_supp = csp_110a,
         fin_supp_child_exp = csp_110b,
         fin_supp_lump = csp_110c,
         fin_supp_other = csp_110d,
         fin_supp_agreement = csp_160,
         future_children_intention = fi_110) 
```

```{r,include=FALSE}
# Final clean up
reduced_census <- 
  gss %>%
  mutate(bornin_canada =
           if_else(place_birth_canada=="Born in Canada","Yes",
                   if_else(place_birth_canada=="Born outside Canada","No", "Don't know/ Prefer not to say"))) %>%
  mutate(age2019 = age+2) %>%
  mutate(age_group= cut(age2019, 
                          breaks=c(18,34, Inf),
                          labels=c('18-34 youth', '35+ elder'))) %>% 
  clean_names() %>% 
  rename(gender = sex) %>% 
  select(gender,
         age_group,
         province,
         bornin_canada)
reduced_census <- na.omit(reduced_census)

new_census <- 
  reduced_census%>%
  count(gender, province, age_group,bornin_canada) %>%
  group_by(gender, province, age_group,bornin_canada) 

write_csv(new_census, "gss.csv")
```

```{r, include=FALSE}
# Loading in the cleaned survey Data
survey_data <- read.csv("survey_data.csv")

# Loading in the cleaned census Data
census_data <- read_csv("gss.csv")

```

Survey data:
```{r,echo=FALSE}
head(survey_data)
```

Census data:
```{r,echo=FALSE}
head(census_data)
```



## 2.2 Logistic Model
As the propose of building models in this section is to find out the relationship between the dependent binary variable of vote choice and four independent predictors, logistic regression models would be considered as a good choice to model dichotomous outcome variables. Additionally, the log odds of the logistic result display the linear combination of the predictors, which could perform a suitable model outcome for the data.

Then, two logistic regression models will be built to predict the probability of voting Liberals and Conservatives correspondingly.
The general formula of the model will be:
$$ log(\frac{p}{1-p}) = \beta_0+\beta_1  x_{gender} + \beta_2x_{province} + \beta_3x_{agegroup} + \beta_4 x_{bornincanada} $$

The Liberal Party:
```{r,echo=FALSE}
# Creating the Model
logit_model_libr <- glm(vote_liberal ~ as.factor(gender) + as.factor(province)+ as.factor(age_group)+as.factor(bornin_canada), data=survey_data, family='binomial')

# Model Results (to Report in Results section)
summary(logit_model_libr)
```

Firstly, a logistic regression model is built based on the voting intention for Justin Trudeau’s Liberals. This model performs the relationship between the voting intention and predictors directly through specific numbers, where $log(\frac{p}{1-p})$ is the log odd that indicates the change of proportion of voters who will vote for the Liberal Party. The $\beta_0$ is the intercept that point out the possible proportion of voting Trump in log odds when all of the predictors are zero, which is the condition that voters are all females from Alberta with their age between 18 to 34, who are not willing to tell their birthplace. Then, the average difference in log odds of choosing Trudeau between gender is represented by the slope $\beta_1$. To interpret $\beta_2$, for every additional unit increase in a vote from distinct provinces, we expect the log odds of the proportion of voting Liberals to increase by $\beta_2$ unit. Similarly, a variety of differences of vote probabilities on average are predicted by $\beta_3$ and $\beta_4$.


The Conservative Party:
```{r,echo=FALSE}
# Creating the Model
logit_model_cons <- glm(vote_conservative ~ as.factor(gender) + as.factor(province)+ as.factor(age_group)+as.factor(bornin_canada), data=survey_data, family='binomial')

# Model Results (to Report in Results section)
summary(logit_model_cons)
```

What's more, the relationship between prediction variables and the probability of voting Andrew Scheer's Conservatives is present by the second model. The interpretations of predictors are quite similar to those in the previous model. The $log(\frac{p}{1-p})$ is the log odd that indicates the change of proportion of voters who will vote for the Conservative Party. The $\beta_0$ is the intercept that point out the possible proportion of voting Conservatives in log odds when all of the predictors are zero, which is the condition that voters are all females from Alberta with their age between 18 to 34, who are not willing to tell their birthplace. Then, the average difference in log odds of choosing Scheer between gender is represented by the slope $\beta_1$. To interpret $\beta_2$, for every additional unit increase in the vote from distinct provinces, we expect the log odds of a proportion of voting Liberals to increase by $\beta_2$ unit. Similarly, a variety of differences of vote probabilities on average are predicted by $\beta_3$ and $\beta_4$.


## 2.3 Post-Stratification

A post-stratification strategy will be utilized to estimate the probability of voter who votes for two parties. Based on the models above, the relationship between voting preference and predictor variables could be used to estimate the probability of voting for two parties in the entire population. Cells are creating based on different gender, constituencies, age groups and whether voters born in Canada. By adjusting the sampling weights, the estimated proportion of voters that will make a specific choice could be calculated for each bin. In order to get the final estimated result, each proportion estimate will be weighted by the respective population size. Those resulting values will be summed up and then divided by the population size. 

The formula of post-stratification will be: 
$$\hat{Y}^{ps} = \frac{\sum N_j \hat{y_j}}{\sum N_j}$$

The $\hat{y_j}$ on the numerator is the estimate of each bin. The number of voters within each bin is represented by $Nj$ on the numerator, while $N_j$ on the denominator shows the size of entire population. 

```{r,echo=FALSE}
census_data$log_estimate_libr <-
  logit_model_libr %>%
  predict(newdata = census_data)

census_data$estimate_libr <-
  exp(census_data$log_estimate_libr)/(1+exp(census_data$log_estimate_libr))

census_data <-
  census_data %>%
  mutate(alp_predict_prop_libr = estimate_libr*n)
  
alp_predict_libr = sum(census_data$alp_predict_prop_libr)/sum(census_data$n)

```

```{r,echo=FALSE}
census_data$log_estimate_cons <-
  logit_model_cons %>%
  predict(newdata = census_data)

census_data$estimate_cons <-
  exp(census_data$log_estimate_cons)/(1+exp(census_data$log_estimate_cons))

census_data <-
  census_data %>%
  mutate(alp_predict_prop_cons = estimate_cons*n)

alp_predict_cons = sum(census_data$alp_predict_prop_cons)/sum(census_data$n)
 
```


## 2.4 Linear Model with BIC

In order to select useful variables that will affect the voting results indeed, linear models with backward elimination of BIC is also used for the data. Since BIC penalizes model complexity which sets a restriction to avoid the problem of overfitting, a reduced model with necessary variables to fit the model could help to focus on data that have a stronger correlation with outcome.

The Liberal Party:
```{r,include=FALSE}
# Creating the Model
linear_model_libr <- lm(vote_liberal ~ as.factor(gender) + as.factor(province)+ as.factor(age_group)+as.factor(bornin_canada), data=survey_data)
```

```{r,include=FALSE}
n <- nrow(survey_data)
BIC_libr <-  step(linear_model_libr, direction = "backward", k=log(n))
```

```{r,echo=FALSE}
#Model Results
summary(BIC_libr)
```
After the process of BIC, the 'gender' predictor is removed from the linear model of Liberals.



The Conservative Party:
```{r,include=FALSE}
# Creating the Model
linear_model_cons <- lm(vote_conservative ~ as.factor(gender) + as.factor(province)+ as.factor(age_group)+as.factor(bornin_canada), data=survey_data)
```

```{r,include=FALSE}
n <- nrow(survey_data)
BIC_cons <-  step(linear_model_cons, direction = "backward", k=log(n))
```

```{r,echo=FALSE}
#Model Results
summary(BIC_cons)
```
After the process of BIC, the 'bornin_canada' predictor is removed from the Conservatives' fitted model.


# 3. Results
MRP results:
Liberals:
```{r,echo=FALSE}
#liberals
alp_predict_libr
```
Conservatives:
```{r,echo=FALSE}
#conservatives
alp_predict_cons
```

Base on the result of the post-stratification analysis modelled by logistic regression models, which counted for voters' gender, provinces, age groups and whether born in Canada, the estimate proportion of voters who will advocate Justin Trudeau’s Liberals and Andrew Scheer's Conservatives will be 0.2917461 and 0.2713815 respectively. It means that under the condition that every person over 18 has voted, the result of the election will not be different from that in 2019. Justin Trudeau’s Liberals will still gain the most support from citizens.

```{r,echo=FALSE}
kable(summary(logit_model_libr)$coefficients, caption = "Coefficients of Logistic Model of Liberals")
```
From the table, it is clear that four of the estimated parameters are negative and the remaining ones are all positive. The Liberal party could gain more support from citizens if the number of voters from groups with positive parameter increases, as every unit of increase in the positive estimate parameters will lead to an increase in the probability of voting for Liberals. Conversely, parameters with negative estimate might cause a decline in the voting support. According to the p-value of the variables, the predictors 'province' and 'age_group' have a quite small p-value. This result shows that changes in these two variables could influence the outcome of voting strongly, comparing with variables 'gender' and 'bornin_canada'. Specifically, voters from different provinces and age groups have distinct points of view toward whether to vote for Liberals. Females and males with their birthplace inside or outside Canada seem to share equivalent perspective toward the Liberals.

```{r,echo=FALSE}
kable(summary(logit_model_cons)$coefficients, caption = "Coefficients of Logistic Model of Conservatives")
```

While the table of Conservatives is quite different from the one of Liberals. Most of the estimated parameters are negative that could lead to a decline in the voting support. Every unit of increase in the negative estimate parameters will lead to a reduction in the probability of voting for Conservatives. According to the p-value in this table, the predictors 'gender' and 'province' have a quite small p-value.
This result shows that changes in these two variables could affect the outcome of voting strongly, comparing with remaining variables 'age_group' and 'bornin_canada'. To be specific, female and male voters from distinct constituencies will have opposite perspectives toward whether to vote for Liberals. 

BIC results:
Fitted model for Liberals:
```{r,echo=FALSE}
lm(formula = vote_liberal ~ as.factor(province) + as.factor(age_group) 
   + as.factor(bornin_canada), data = survey_data)
```

From BIC formula of the Liberals, the fitted model after using backward elimination of BIC only includes three predictors. Since BIC sets a balance between the goodness of fit and the penalty for model complexity. The 'gender' variable is considered as an unessential predictor that has been removed from the original. 


Fitted model for Conservatives:
```{r,echo=FALSE}
lm(formula = vote_conservative ~ as.factor(gender) + as.factor(province) 
   + as.factor(age_group), data = survey_data)
```

From BIC formula of the Conservatives, the fitted model after using backward elimination of BIC includes three predictors as well. Since BIC sets a balance between the goodness of fit and the penalty for model complexity. The 'bornin_canada' predictor is seemed as a unimportant variable that has been removed from the original. 


# 4. Discussion
## 4.1 Summary
The popular vote outcome of the 2019 Canadian federal election under the condition that everyone over 18 has voted is predicted in this study. To begin with, a cleaned data set from 2019 CES data was used to build logistic models that could demonstrate the probabilities of voting Liberals and Conservatives respectively. Predictors gender, constituency, age group and whether born in Canada were chosen for the models, as these four variables were likely to be influential to voters' outcome. From there, the 2017 GSS data was utilized to estimate the proportion of voters who will vote for each party through the post-stratification analysis. By adjusting weights of samples within each post-stratum of predictors, the proportion of probability of voting Liberals and Conservatives within the entire population will be 0.2917461 and 0.2713815 respectively.

## 4.2 Conclusions
As the estimated proportions of voters in favour of voting for Liberals and Conservatives are 0.2917461 and 0.2713815 respectively, we made a prediction that Trudeau will still likely to win the election like that in the reality. The general result for the election will not be affected even different assumption has made. 

According to the Global News polling conducted by Ipsos, the support seems to be similar for the Liberal Party regardless of age or gender, but quite different for the Conservatives (Ipsos, 2019). Models built by MRP and BIC in the previous parts confirm this idea. For the winner Liberals, females and males seem to share equivalent perspective toward the Liberals. However, Trudeau should be aware of the support from provinces like Ontario, British Columbia, New Brunswick, Newfoundland and Quebec. These constituencies with extremely small p-values in the model could cause a huge impact on the result. If Liberals suffer losses in these regions of the country, Conservatives might make inroads. While for the Conservative Party, Scheer might win a majority of male. The reason that he lose supports from women might be his affirmation of opposing abortions and same-sex marriages (Global News,2019). This argument displays an attitude that refuses to protect the rights of Canadian women and LGBTQ2 individuals, which may cause women and LGBTQ2 individuals to resent him and cause his election to be unsatisfactory.

Therefore, the proportions of voter turnout could be very significant to the final outcome of the election. The one that gains more support from citizens should be aware of the rights of individuals from a variety of perspectives. As the voting intentions of male and female in distinct segmenting generations were quite different, the leader of one nation should provide support especially for the minority like female and LGBTQ2 individual. Otherwise, the result is not likely to be satisfied.

## 4.3 Weaknesses
The relationship between voters' characterization and the outcome of the election has been demonstrated. Additionally, the estimate proportion of voting and the prediction base on the results were made. Nevertheless, some limitations and drawbacks might appear for the analysis.

1. Only four predictors were used to fit the model due to the limit of time and technique. Some other important variables that could make a huge impact on the outcome of voting might fall into neglect, such as race, ethnicity and education levels. This could lead to an imprecise analysis of the result.

2. General factors were used to replace some variables in details in order to make the model-building procedure more convenient. Detailed factors could provide the analysis with more precise information of the voters. Some factors might have strong relationships with the final outcome.

3. The raw data set was downloaded online, the phone survey data was not included in this data set. Then the analysis might not be comprehensive enough since partial information was ignored in the first stage.

4. Some other factors might appear to influence the interactions between gender, province, age groups, whether born in Canada and vote choice. For example, choices of family numbers and friends might change one's vote intention to the opposite and eventually vote for the other party than the original.

5. As Canada has a parliamentary system, the popular support cannot decide the final result of the prime minister. Winning seats in parliament determine the party that could have control of the executive. Therefore, the final outcome cannot be predicted simply by current data.

## 4.4 Next Steps
Improvements could be made to complement the conclusions of this report in the next steps.

1. A follow-up survey could be made to make the coverage of information more precisely. The survey should be delivered through multiple channels including website, phone, mails and so on.

2. Some other factors that might impact the preference of voter should be considered. Employment status could cause different policies on social welfare that may lead to distinct opinions toward parties. What's more, educational status causes perspectives toward campaign promises of candidates to be different. These factors seem to be crucial to the analysis as well. 

3. Beside those NA cases in the data set, some outliers and extreme cases that might be influential to the model should be detected in order to make a more precise prediction.

4. A post-hoc analysis that compare the differences between this analysis and the actual election results could be made. Further identification could help to improve the estimation of the next election. 

# 5. References
Andrew. (2020, January 10). Linear or logistic regression with binary outcomes. Retireved from https://statmodeling.stat.columbia.edu/2020/01/10/linear-or-logistic-regression-with-binary-outcomes/. 

Connolly, A. (2019, October 03). Andrew Scheer confirms he remains 'pro-life' when asked about abortion. Retrieved December 17, 2020, from https://globalnews.ca/news/5985083/andrew-scheer-pro-life/

Factors associated with voting. (2015, November 27). Retrieved December 09, 2020, from https://www150.statcan.gc.ca/n1/pub/75-001-x/2012001/article/11629-eng.htm

Federal election 2019 live results. (n.d.). Retrieved December 09, 2020, from https://newsinteractives.cbc.ca/elections/federal/2019/results/

Masters, A. (2019, November 27). MRP Estimates and the 2019 General Election. Retrieved December 09, 2020, from https://anthonybmasters.medium.com/mrp-estimates-and-the-2019-general-election-9ac1794120d6

R Core Team (2019). R: A language and environment for statistical computing. R Foundation for
  Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.
  
R Pruim (2016). Mathematics in R Markdown. Retrieved from https://rpruim.github.io/s341/S19/from-class/MathinRmd.html

Significant Gender Gap in Voting Intentions Among Younger Canadians; Boomers Vote as Block, Regardless of Gender. (n.d.). Retrieved December 09, 2020, from https://www.ipsos.com/en-ca/news-polls/Significant-Gender-Gap-in-Voting-Intentions-Among-Younger-Canadians

Stephenson, Laura B; Harell, Allison; Rubenson, Daniel; Loewen, Peter John, 2020, '2019 Canadian Election Study - Online Survey', https://doi.org/10.7910/DVN/DUS88V, Harvard Dataverse, V1

Stephenson, Laura, Allison Harrel, Daniel Rubenson and Peter Loewen. Forthcoming. 'Measuring Preferences and Behaviour in the 2019 Canadian Election Study,' Canadian Journal of Political Science.

Welcome to the 2019 Canadian Election Study. (n.d.). Retrieved December 09, 2020, from http://www.ces-eec.ca/

Yihui Xie (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package
  version 1.28.
